Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-06-11 paper/1_Initial/manuscript.qmd
fix bold

table <- data.frame(
  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', '***Total***'),
  Samples = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "\\textbf{31317}"),
  Age = c('', "25.8 ± 8.4 [18-69]", 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
  SD = c('', 8.4, 16.9, 5.3, 10.5, 12.41, 27.5, 14.5,'',  6.7, 12.6, 9.3, '', 8.4, 7.4, 14.4, 10.1, 13.2, 13.2),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
  Link= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'In preparation **', 'In preparation **', '')
)

knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
  kableExtra::kable_styling(font_size = 7)
```

>>>>

table <- data.frame(
  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Total'),
  Samples = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "31317"),
  Age = c('', "25.8 ± 8.4 [18-69]", 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
  SD = c('', 8.4, 16.9, 5.3, 10.5, 12.41, 27.5, 14.5,'',  6.7, 12.6, 9.3, '', 8.4, 7.4, 14.4, 10.1, 13.2, 13.2),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
  Link= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'In preparation **', 'In preparation **', '')
)

knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, 
             col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
  kableExtra::kable_styling(font_size = 7) |> 
  kableExtra::row_spec(0, bold=TRUE) |> 
  kableExtra::row_spec(nrow(table), bold=TRUE, italic=TRUE)
```
